Running simulations of MultipleContactNeutralMigrat.nlogo

### 2024-08-02 RunSims.Rmd
New simulations with deforestation-at-time=600

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 200 for lambda=4 ) 
* Check simulations with Migration0-at-deforestation true or false to take into account that immigration happens at the borders and different kinds of deforestation patterns have different border size e.g. regular > randon block

```{r SLOSS_lambda14_sims_regular,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf06_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

## Read Simulations

```{r readSimulations, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

mdl <- read_sloss_simul(outpath,"NoSelection_pf06_hps3-61_dd1-3_brb1-4_regular_ff.csv")

netlogo_evaluate_patch_distr(mdl$find_cluster_sizes[1])

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf04-08_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

@@

## Lambda = 1-4 / Random Block patterns

```{r SLOSS_lambda14_simulations_block,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf06_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path", "find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

## Read Simulations No Selection Random Block Patterns prob-frag = 0.6

```{r readSimulationsBlock, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_sloss_simul(outpath,"NoSelection_pf06_hps3-61_dd1-3_brb1-4_block_ff.csv")

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf04_08_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path", "find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                               "prob-frag" =  list(values=c(0.4,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

@@

```{r Hierarchical_SLOSS_lambda14_pf48_simulations_regular,echo=FALSE,message=FALSE,warning=FALSE,eval=TRUE}

@@

# Plot for hierarchical communities

@@

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="Hierarchical", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(birds_at_deforestation:count_birds,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

@@

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/Hierarchical_Species_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.94,0.83)
    )

ggsave("Figures/Hierarchical_Shannon_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

@@

## Read Simulations Birth Selection  regular Patterns

@@

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_sloss_simul(outpath,"Selection_pf06_hps3-61_dd1-3_brb1-4_regular_ff.csv")

@@

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="BirthSelection", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds) %>% summarise(across(birds_at_deforestation:count_birds,list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) ))) #  %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )
names(mdl1)

mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/Selection_Species_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.9,0.8)
    )

ggsave("Figures/Selection_Shannon_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

>>>>

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 600 for lambda=4 ) 
* Check simulations with Migration0-at-deforestation true or false to take into account that immigration happens at the borders and different kinds of deforestation patterns have different border size e.g. regular > randon block

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf04-08_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 600,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

@@

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf04_08_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path", "find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                               "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 600,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

@@

```{r Hierarchical_SLOSS_lambda14_pf48_simulations_regular,echo=FALSE,message=FALSE,warning=FALSE,eval=FALSE}

@@

## Read Simulations hierarchical regular Patterns prob_frag 0.4 - 0.8

```{r readSimulationsHierarchicalRegular_pf48, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_sloss_simul(outpath,"Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_regular_ff.csv")

## Simulations Lambda = 1-4 / Random Block - Hierarchical communities / prog-frag 0.4-0.6-0.8

```{r Hierarchical_SLOSS_lambda14_pf48_simulations_block,echo=FALSE,message=FALSE,warning=FALSE,eval=FALSE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"Hierarchical\"",
                                             "replacement-rate" = 0.3
                                             ))

## Read Simulations hierarchical random-block Patterns prob_frag 0.4 - 0.8

```{r readSimulationsHierarchicalBlock_pf48, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_sloss_simul(outpath,"Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_block_ff.csv")

# Plot for hierarchical communities Regular pattern

@@

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="Hierarchical", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds,prob_frag) %>% summarise(across(c(birds_at_deforestation:count_birds,mean_patch,degraded_mfp,non_degraded_mfp),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) )))

@@

mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_Species_Dispersal_pf_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Hierarchical_Shannon_Dispersal_pf_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

# Plot for hierarchical communities random block pattern

```{r ExploratoryPlotsHierarchicalBlock, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- sloss_sim %>% filter(deforestation_type == "random block", birds_behavior=="Hierarchical", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds,prob_frag) %>% summarise(across(c(birds_at_deforestation:count_birds,mean_patch,degraded_mfp,non_degraded_mfp),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) )))

mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_Species_Dispersal_pf_Lambda_block.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Hierarchical_Shannon_Dispersal_pf_Lambda_block.png",width=8,height=6,units="in",dpi=600)

@@

## Simulations Lambda = 1-4 / Regular patterns - Birth Selection communities / prog frag 0.4-0.8

```{r Selection_SLOSS_lambda14_pf48_regular,echo=FALSE,message=FALSE,warning=FALSE,eval=FALSE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Selection_pf04-08_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                               "prob-frag" =  list(values=c(0.4,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"BirthSelection\"",
                                             "replacement-rate" = 0.3
                                             ))

## Simulations Lambda = 1-4 / random block patterns - Birth Selection communities / prog frag 0.4-0.8

```{r Selection_SLOSS_lambda14_pf48_block,echo=FALSE,message=FALSE,warning=FALSE,eval=FALSE}

# pf = probability of fragmentation
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Selection_pf04-08_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                               "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"BirthSelection\"",
                                             "replacement-rate" = 0.3
                                             ))

## Read Simulations Birth Selection  regular & random block Patterns

@@

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
# Ya leimos este ->
# mdl <- read_sloss_simul(outpath,"Selection_pf06_hps3-61_dd1-3_brb1-4_regular_ff.csv")
#
# sloss_sim <- bind_rows(sloss_sim,mdl)

mdl <- read_sloss_simul(outpath,"Selection_pf04-08_hps3-61_dd1-3_brb1-4_regular_ff.csv")

mdl <- read_sloss_simul(outpath,"Selection_pf04-08_hps3-61_dd1-3_brb1-4_block_ff.csv")

# Check simulations in mdl
mdl %>% distinct(prob_frag,deforestation_type,birds_behavior)

# Check simulations in sloss_sim
sloss_sim %>% distinct(prob_frag,deforestation_type,birds_behavior) %>% arrange(prob_frag,deforestation_type,birds_behavior)

@@

mdl <- sloss_sim %>% filter(deforestation_type == "regular", birds_behavior=="BirthSelection", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds,prob_frag) %>% summarise(across(c(birds_at_deforestation:count_birds,mean_patch,degraded_mfp,non_degraded_mfp),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) )))

#
mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Selection_Species_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Selection_Shannon_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

# Plot for birth selection communities random block patterns

```{r ExploratoryPlotsSelectionBlock, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- sloss_sim %>% filter(deforestation_type == "random block", birds_behavior=="BirthSelection", habitat_patch_size != 199)
names(mdl)
#
# summarize data 
#
mdl1 <- mdl %>% mutate(habitat_patch_size = habitat_patch_size+1) %>%
                         group_by(birds_dispersal_distance, habitat_patch_size,birth_rate_birds,prob_frag) %>% summarise(across(c(birds_at_deforestation:count_birds,mean_patch,degraded_mfp,non_degraded_mfp),list(mean=mean, sd=sd, ql=~quantile(.x,probs=c((1-0.95)/2)), qh=~quantile(.x,probs=c(1-(1-0.95)/2)) )))

#
mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Selection_Species_Dispersal_Lambda_pf_block.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Selection_Shannon_Dispersal_Lambda_pf_block.png",width=8,height=6,units="in",dpi=600)
